Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-11 awipev-CO2.Rmd

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
# 
#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
#     dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
#   dyLegend(show = "auto")   %>%
#   dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y",valueRange = c(-2, 2))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

2015-11-18
, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.

@@

2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
save(file= paste0(path, "fb_data/d_all.rds"), d_all)
```

@@

### ***p*CO~2~**
- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

>>>>

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

2015-11-18
, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23.

@@

2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23.

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
```

@@

### ***p*CO~2~**
- **2020-03-11**: Post calibration parameters for period 4 (2018-04-16 to 2018-10-31) were not taken in consideration because they lead to wrong correction.
- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
